{\normalsize Seminar: Formal Specification} \\[1ex] Security of Multithreaded Programs by Compilation\cite{Barthe07}

### 2012-01-23 paper/paper.tex
made sentence more clear
added first paragraph about execution

The \textit{hidden} threads are the ones we have to care about. These contain
obviously high information in the current program point, but have afterwards
instructions that deal with low information. Since the attacker can watch the
low part of the memory, chances are good that he can deduce high information
through changing low outputs. To prevent indirect flows that are introduced by
these hidden threads, the scheduler will be modified to treat these threads
in a special way. This will be done by 'hiding' these threads, therefore comes
the name of them.

@@

\todo{Explain how the programs are executed}

>>>>

The \textit{hidden} threads are the ones we have to care about. These contain
obviously high information in the current program point, but have afterwards
instructions that deal with low information. Since the attacker can watch the
low part of the memory, chances are good that he can deduce high information
through looking at changing low outputs. To prevent indirect flows that are introduced by
these hidden threads, the scheduler will be modified to treat these threads
in a special way. This will be done by 'hiding' these threads, therefore comes
the name of them.

@@

\todo{Explain how the programs are executed}
To define what noninterference means we need a notion of excution. It is assumed
that we have a sequential execution relation $\leadsto_{seq} \subseteq SeqState \times
SeqState$. The one step execution for the multithreaded language $\leadsto_{seq}
\subseteq (ConcState \times History) \times (ConcState \times History)$ is defined
by the following rules.
